Choose a License

### 2024-09-21 choose_license.qmd
Fix typo

Whenever you create a literary or artistic work (such as a text, image, video, or software), the copyright law in most countries limits other people from copying, modifying, and sharing it without your express permission. [If the work was created as part of your job, it might be your employer who holds the copyright to the work, depending on the country and contract.]{.aside} This even applies if you make it available to others (e.g., on your website): First and foremost they are not allowed to copy, modify, or share it. This legal default of "all rights reserved" was created to benefit publishers, not authors, [@Fogel2006] and runs counter to many cultural and scientific processes. Copyright licenses enable authors to free up their works for reuse by others.

>>>>

Whenever you create a literary or artistic work (such as a text, image, video, or software), the copyright law in most countries limits other people from copying, modifying, and sharing it without your express permission. [If the work was created as part of your job, it might be your employer who holds the copyright to the work, depending on the country and contract.]{.aside} This even applies if you make it available to others (e.g., on your website): First and foremost they are not allowed to copy, modify, or share it. This legal default of "all rights reserved" was created to benefit publishers, not authors [@Fogel2006], and runs counter to many cultural and scientific processes. Copyright licenses enable authors to free up their works for reuse by others.
